---
title: "RLohiya Assignment10"
author: "Ritesh Lohiya"
date: "November 1, 2018"
output: html_document
---

#                             ASSIGNMENT 10

#           IS 605 FUNDAMENTALS OF COMPUTATIONAL MATHEMATICS

Smith is in jail and has 1 dollar; he can get out on bail if he has 8 dollars. A guard agrees to make a series of bets with him. If Smith bets A dollars,
he wins A dollars with probability .4 and loses A dollars with probability .6. 

Find the probability that he wins 8 dollars before losing all of his money if

(a) he bets 1 dollar each time (timid strategy).

```{r}
a <- 0.4
b <- 0.6
c <- b/a


for (i in 0:8){
p <- round((1-c^i)/(1-c^8),4)
print(p)
}
```

P is 0.0203


(b) he bets, each time, as much as possible but not more than necessary to bring his fortune up to 8 dollars (bold strategy).

```{r}
s <- matrix(c(1,0.6,0.6,0.6,0,0,0,0,0,0,0,0.4,0,0,0,0,0,0.4,0,0,0,0,0,0.4,1),nrow = 5, byrow=FALSE)
s

s1 <- matrix(c(0,1,0,0,0),nrow=1)
s1

s2 <- s1 %*% s
s2


s3 <- s2 %*% s
s4 <- s3 %*% s
s4

```
(c) Which strategy gives Smith the better chance of getting out of jail?

Answer: bold strategy gives Smith the better chance of getting out of jail